Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-03-08 draft.tex
expand lemma 2, add new paragraph immediately after w/explanation

\begin{lemma}
When Restriction (\ref{res:3}) of Definition 1 holds, the patron's willingness to invest to maintain the status quo is sufficient to deter the international community from intervening to encourage reunification.
\end{lemma}

\noindent Restriction (\ref{res:3}) provides a bound on the amount that player $p$ must be \emph{willing} to invest each period in order to prevent player $c$ from contesting the status quo outcome. To complete the equilibrium construction, we must determine the utility maximizing investments by $p$ and conditions to ensure that it is \emph{able} to make those investments.\footnote{Efforts by the patron to create the conditions for the \emph{Recognition} outcome are addressed in Lemma 3 once the equilibrium investments are established.}

>>>>

\begin{lemma}
When Restrictions (\ref{res:new}) and (\ref{res:3}) of Definition 1 hold, the patron's willingness to invest to maintain the status quo is sufficient to both deter the international community from intervening to encourage reunification and to avoid the secessionists choosing to go to war.
\end{lemma}

\noindent Restriction (\ref{res:new}) guarantees one of two outcomes: either the patron is willing to invest in the secessionists' status quo payoffs to avoid them falling below the expected payoffs from war or the secessionists' payoffs from war remain below those from ceding so that it is only the patron's incentives concerning the ceding outcome with which we must be concerned. The following treats the latter case; a parallel argument using Restriction \ref{res:new}(b) can be made in the former case.

Restriction (\ref{res:3}) provides a bound on the amount that player $p$ must be \emph{willing} to invest each period in order to prevent player $c$ from contesting the status quo outcome. To complete the equilibrium construction, we must determine the utility maximizing investments by $p$ and conditions to ensure that it is \emph{able} to make those investments.\footnote{Efforts by the patron to create the conditions for the \emph{Recognition} outcome are addressed in Lemma 3 once the equilibrium investments are established.}
